### 2015-10-09 manuscript.Rnw
add Joseph and David as authors

\noindent{\normalsize \sc Fran\c{c}ois Michonneau}\\
\noindent {\small \it $^1$Florida Museum of Natural History \& Whitney Laboratory
  for Marine Sciences, University of Florida, Gainesville,
  FL 32611-7800, USA}\\
\end{center}
\medskip

>>>>

\noindent{\normalsize \sc Fran\c{c}ois Michonneau$^1$, Joseph Brown$^2$, David Winter$^3$}\\
\noindent {\small \it $^1$Florida Museum of Natural History \& Whitney
  Laboratory for Marine Sciences, University of Florida, Gainesville,
  FL, USA}\\
\noindent{\small \it $^2$University of Michigan, Ann Arbor, MI, USA} \\
\noindent{\small \it $^3$Arizona State University, Tempe, AZ, USA} \\
\end{center}
\medskip
